---
title: "Static HTML Report"
author: "Daniel T. Holmes, MD"
date: "29/09/2021"
output:
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
```

## This is a section header

We can insert code into named chunks of R code and expose them or not using the parameter `echo = TRUE` or `echo = FALSE`.

```{r readqcdata, echo = TRUE}
library(readr)
library(dplyr)
library(lubridate)
qc_data <- read_csv("qc_data.csv")
```

## Inline calculations

There are `r nrow(qc_data)` QC results in this file for the following qc codes: `r paste(unique(qc_data$test_code), sep = ",")` for hospitals `r paste(unique(qc_data$hospital), sep = " and ")`. The date range is from `r min(date(qc_data$date_performed))` to `r max(date(qc_data$date_performed))`.

## Tabular Summary of QC Data

Here we can create a table of aggregated statistics of our QC data.

```{r summary, }
sum_table <- qc_data %>%
  group_by(hospital, test_code, qc_name) %>%
  summarise(obs_mean = round(mean(result),1), obs_sd = round(sd(result),1), obs_cv = round(obs_sd/obs_mean*100, 1), set_mean = round(mean[1],1), set_sd = sd[1], set_cv = round(set_sd/set_mean*100,1))

library(kableExtra)
kable(sum_table) %>%
    kable_styling(bootstrap_options = c("striped", "hover"))
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

## Graphical Summary of Our Creatinine QC

```{r ljplotcr1, fig.height=4, fig.width=8}
library(lubridate)
library(ggplot2)

cr_stats<- qc_data %>%
  filter(test_code == "CRQ") %>%
  group_by(qc_name) %>%
  summarise(obs_mean = round(mean(result),1), obs_sd = round(sd(result),1), obs_cv = round(obs_sd/obs_mean*100, 1), set_mean = round(mean[1],1), set_sd = sd[1], set_cv = round(set_sd/set_mean*100,1))

cr1 <- qc_data %>%
  mutate(rundate = date(ymd_hms(date_performed))) %>%
  filter(hospital == "SPH", test_code == "CRQ", qc_name == "CH1") %>%
  group_by(qc_name, rundate) %>% 
  ggplot(aes(x = rundate,y = result)) +
  geom_point(alpha = 0.3) +
  geom_hline(yintercept = cr_stats$obs_mean[1], col = "blue") + 
  geom_hline(yintercept = cr_stats$obs_mean[1] + 1.96*cr_stats$obs_sd[1], col = "red", linetype = "dashed") + 
  geom_hline(yintercept = cr_stats$obs_mean[1] - 1.96*cr_stats$obs_sd[1], col = "red", linetype = "dashed") + 
  ylim(c(cr_stats$obs_mean[1] - 3*cr_stats$obs_sd[1],cr_stats$obs_mean[1] + 3*cr_stats$obs_sd[1])) +
  ggtitle("Creatinine Level 1") + 
  facet_wrap(~instr_code)

cr1
```

```{r ljplotcr2, fig.height=4, fig.width=8}
cr2 <- qc_data %>%
  mutate(rundate = date(ymd_hms(date_performed))) %>%
  filter(hospital == "SPH", test_code == "CRQ", qc_name == "CH2") %>%
  group_by(qc_name, rundate) %>% 
  ggplot(aes(x = rundate,y = result)) +
  geom_point(alpha = 0.3) +
  geom_hline(yintercept = cr_stats$obs_mean[2], col = "blue") + 
  geom_hline(yintercept = cr_stats$obs_mean[2] + 1.96*cr_stats$obs_sd[2], col = "red", linetype = "dashed") + 
  geom_hline(yintercept = cr_stats$obs_mean[2] - 1.96*cr_stats$obs_sd[2], col = "red", linetype = "dashed") +
  ylim(c(cr_stats$obs_mean[2] - 3*cr_stats$obs_sd[2],cr_stats$obs_mean[2] + 3*cr_stats$obs_sd[2])) +
  ggtitle("Creatinine Level 2") +
  facet_wrap(~instr_code)

cr2
```
